A decomposition Approach for solving the JSP using multi-shot ASP\thanks{Supported by organization x.}

### 2022-01-16 ICLP Paper/samplepaper.tex
added some literature

>>>>

In real-world production scheduling, the number of operations to process can easily go
into tens of thousands \citep{coltep19a,kohakamo20a,kotakoscge21a}, which exceeds exact
optimization capacities even of state-of-the-art solvers for Answer Set Programming (ASP),
Mixed Integer Programming (MIP), or Constraint Programming (CP)
\citep{daneshamooz2021mathematical,francescutto2021solving,shi2021solving}.
